Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Respond to review wrt stack of tasks.

The equivalent random  extension on a constrained manifold $\manifold$, 
defined by the constraint function $f$,
starts from a valid configuration $q_{near} \in \manifold$, and extends the tree
towards a random configuration $q_{rand}$, while keeping the constraints
satisfied. Extension attempts orthogonal to $\manifold$ are useless,
as newly added edges have to be included  in $\manifold$. To extend in directions
that follow the directions of $\manifold$, we rely on the framework of 
Jacobian-based prioritized inverse kinematics. Algorithm~\ref{alg:constrained} presents
the adaptation of the classic extend function, and Fig.~\ref{fig:gikrrt} illustrates this
extension. The idea is to first project $q_{rand}$ on the tangent
space to $\manifold$  at $q_{near}$. Let us call the projected configuration $q_{rand}'$.
$q_{rand}'$ is obtained by one step of prioritized inverse kinematics optimization. Let 
$q_{rand}''$  be the result of a call to $\texttt{SolveConstraints}(q_{rand}',f,\epsilon)$.  It is 
the projection
of $q_{rand}'$ on $\manifold$. Instead of extending the tree from $q_{near}$ towards 
$q_{rand}$, the algorithm tries to extend from $q_{near}$ towards 
$q_{rand}''$\footnote{This presentation attempts to give a precise idea of the algorithm, without 
  focusing on technical details. Readers interested in the actual implementation can
  refer to \url{https://github.com/laas/hpp-constrained} and 
  \url{https://github.com/laas/hpp-constrained-planner}, where the corresponding open-source 
  code is available.}. While extending the tree,
the configurations along the new edge are automatically projected onto $\manifold$. These projections 
are not very costly if the edge is close to the constrained manifold.

@@

\end{tikzpicture}
\end{minipage}
\begin{minipage}[c]{0.3\linewidth}
\begin{tikzpicture}[x=0.61cm,y=0.61cm]
   \definecolor{dg}{rgb}{0,0.3,0}
      %Stack of tasks:
      \draw [color=black, thick,fill = white] (0,1) rectangle (2,2);
      \draw [color=black, thick,fill = white] (0,2) rectangle (2,3);
      \draw [color=black, thick,fill = white] (0,3) rectangle (2,5);
      \draw [color=black, thick,fill = white] (0,5) rectangle (2,6);
      \draw [color=black, thick,fill = white] (0,6) rectangle (5,7);
      \draw [color=black, thick,fill = white] (1,1) rectangle (5,6);
      \draw [thick] (1,1) -- (5,1) -- (5,6);
      \draw (1,2) -- (5,2) ;
      \node [text width = 5cm,text centered] at (2.5,6.5) {\large Stack
        of tasks};
      \begin{scriptsize}
        \node at (0.5,5.5) {1};
        \node at (0.5,4) {$\vdots$}; 
        \node at (0.5,2.5) {$n$};
        \node at (0.5,1.5) {$n$+1};

        \node [text width = 2cm,color=dg] at (3.2,4) {\small Constraints defining
          $\manifold$};
        \node [text width = 3cm,text centered] at (3,1.5)
              { Configuration task towards $q_{rand}$};    
      \end{scriptsize}

\end{tikzpicture}
\end{minipage}

\caption{One step of constrained extension, and the stack of tasks used
  to generate $q_{rand}'$ with a prioritized inverse kinematics solver, 
  starting from $q_{near}$:
  first, the constraints defining $\manifold$, and at a lower priority
  a configuration task towards $q_{rand}$.  $q_{rand}'$ is then projected onto
  $\manifold$, and a classic RRT extension tries to go as far as possible
  from $q_{near}$ towards $q_{rand}''$.}
\label{fig:gikrrt}
\end{figure}

@@

The  algorithm   that  animates  a  statically  balanced   path  into  a
dynamically balanced  walk trajectory has been inspired  by the previous
small-space controllability  proof.
Given a statically  balanced path $p$ respecting the cart-table model approximation constraints,
we  start  by placing  footprints  corresponding  to  the nominal  walk
pattern  of the  robot. Given the footprints, we  compute a ZMP trajectory, 
and a preview controller outputs  a corresponding CoM trajectory. 
The stack of tasks applied to
the robot to generate a dynamic walk motion is -- in decreasing priority order:

@@

\STATE $DynamicTrajectory \leftarrow \text{Animate}(StackOfTasks)$

>>>>

The equivalent random extension on a constrained manifold $\manifold$,
defined by the constraint function $f$, starts from a valid
configuration $q_{near} \in \manifold$, and extends the tree towards a
random configuration $q_{rand}$, while keeping the constraints
satisfied. Extension attempts orthogonal to $\manifold$ are useless,
as newly added edges have to be included in $\manifold$. To extend in
directions that follow the directions of $\manifold$, we rely on
Jacobian-based inverse kinematics. Algorithm~\ref{alg:constrained}
presents the adaptation of the classic extend function, and
Fig.~\ref{fig:gikrrt} illustrates this extension. The idea is to first
project $q_{rand}$ on the tangent space to $\manifold$ at
$q_{near}$. Let us call the projected configuration $q_{rand}'$. Let
$q_{rand}''$ be the result of a call to
$\texttt{SolveConstraints}(q_{rand}',f,\epsilon)$.  It is the
projection of $q_{rand}'$ on $\manifold$. Instead of extending the
tree from $q_{near}$ towards $q_{rand}$, the algorithm tries to extend
from $q_{near}$ towards $q_{rand}''$ while remaining on
$\manifold$ \footnote{This presentation attempts to give a precise
  idea of the algorithm, without focusing on technical
  details. Readers interested in the actual implementation can refer
  to \url{https://github.com/laas/hpp-constrained} and
  \url{https://github.com/laas/hpp-constrained-planner}, where the
  corresponding open-source code is available.}. While extending the
tree, the configurations along the new edge are automatically
projected onto $\manifold$. These projections are not very costly if
the edge is close to the constrained manifold.

@@

\end{tikzpicture}
\end{minipage}
\begin{minipage}[c]{0.3\linewidth}
%% \begin{tikzpicture}[x=0.61cm,y=0.61cm]
%%    \definecolor{dg}{rgb}{0,0.3,0}
%%       %Stack of tasks:
%%       \draw [color=black, thick,fill = white] (0,1) rectangle (2,2);
%%       \draw [color=black, thick,fill = white] (0,2) rectangle (2,3);
%%       \draw [color=black, thick,fill = white] (0,3) rectangle (2,5);
%%       \draw [color=black, thick,fill = white] (0,5) rectangle (2,6);
%%       \draw [color=black, thick,fill = white] (0,6) rectangle (5,7);
%%       \draw [color=black, thick,fill = white] (1,1) rectangle (5,6);
%%       \draw [thick] (1,1) -- (5,1) -- (5,6);
%%       \draw (1,2) -- (5,2) ;
%%       \node [text width = 5cm,text centered] at (2.5,6.5) {\large Stack
%%         of tasks};
%%       \begin{scriptsize}
%%         \node at (0.5,5.5) {1};
%%         \node at (0.5,4) {$\vdots$}; 
%%         \node at (0.5,2.5) {$n$};
%%         \node at (0.5,1.5) {$n$+1};

%%         \node [text width = 2cm,color=dg] at (3.2,4) {\small Constraints defining
%%           $\manifold$};
%%         \node [text width = 3cm,text centered] at (3,1.5)
%%               { Configuration task towards $q_{rand}$};    
%%       \end{scriptsize}

%% \end{tikzpicture}
\end{minipage}

\caption{\textbf{One step of constrained extension illustrating
    Algorithm \ref{alg:constrained}: $q_{rand}$ is first projected on
    the tangent space of $\manifold$. $q_{rand}'$ is then projected
    onto $\manifold$, and a classic RRT extension tries to go as far
    as possible from $q_{near}$ towards $q_{rand}''$ while remaining
    on $\manifold$. $q_{new}$ is then returned.}}
\label{fig:gikrrt}
\end{figure}

@@

The algorithm that animates a statically balanced path into a
dynamically balanced walk trajectory has been inspired by the previous
small-space controllability proof. \textbf{Given a statically balanced
  path $p$ verifying the cart-table model approximation constraints,
  we start by placing footprints corresponding to the nominal walk
  pattern of the robot. Given the footprints, we compute a ZMP
  trajectory, derive foot trajectories, and a preview controller
  outputs a corresponding CoM trajectory. Classic numerical
  Jacobian-based prioritized inverse kinematics methods prove to be
  very useful to generate a dynamic walking trajectory while trying to
  accomplish secondary tasks, such as following a reference
  configuration trajectory. We use the same framework which was
  developped in \cite{yoshida2006tds}.}

The stack of tasks applied to the robot to generate a dynamic walking
motion is -- in decreasing priority order:

@@

\STATE $DynamicTrajectory \leftarrow
\text{ComputeWalkTrajectory}(StackOfTasks)$
